---
title: "Article Title"
author: 
  - name: "Author Name"
    affiliation: "Institution"
    email: "author@email.com"
date: "`r Sys.Date()`"
output:
  html_document:
    keep_md: true
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    highlight: tango
    fig_caption: true
  pdf_document:
    toc: true
    number_sections: true
bibliography: references.bib
csl: mla.csl
jekyll_front_matter:
  layout: page
  category: "section1"
  type: "issue01"
  issue: "01"
  year: "2024"
  DOI: "xxx.xxx"
  title: "Article Title"
  bio: ["author1"]
  description: "Short description for metadata and social media"
  media:
    - path: "path/foldername/"
      default: "image.jpg"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 8,
  fig.height = 6,
  fig.align = "center",
  dpi = 300
)

# Load required libraries
library(ggplot2)
library(dplyr)
library(knitr)
library(plotly)
library(DT)
```

# Abstract

Write your abstract here. This template demonstrates how to use R for data analysis within an academic journal article that will be published using Jekyll.

**Keywords:** R, data analysis, academic publishing, Jekyll, digital humanities

# Introduction

This R Markdown template allows authors to create data-driven academic articles that can be seamlessly integrated into the Jekyll journal system. The template supports:

- Data analysis and visualization using R
- Automatic citation formatting
- Interactive plots and tables
- Reproducible research practices

# Data Analysis

## Loading and Exploring Data

```{r data-loading}
# Generate sample dataset for demonstration
set.seed(123)
sample_data <- data.frame(
  year = rep(2018:2023, each = 50),
  category = sample(c("Digital Humanities", "Media Studies", "Cultural Studies"), 300, replace = TRUE),
  value = rnorm(300, mean = 50, sd = 15),
  impact_factor = runif(300, min = 1, max = 5)
)

# Display basic statistics
kable(summary(sample_data), caption = "Summary Statistics of Sample Data")
```

## Visualization

### Static Plots

```{r static-plot}
# Create a static visualization
trend_plot <- ggplot(sample_data, aes(x = year, y = value, color = category)) +
  geom_smooth(method = "loess", se = FALSE) +
  geom_point(alpha = 0.6) +
  labs(
    title = "Trends in Academic Research Areas",
    x = "Year",
    y = "Research Output Value",
    color = "Category"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    legend.position = "bottom"
  )

print(trend_plot)
```

### Interactive Plots

```{r interactive-plot}
# Create an interactive visualization
interactive_plot <- plot_ly(
  data = sample_data,
  x = ~year,
  y = ~value,
  color = ~category,
  type = "scatter",
  mode = "markers",
  marker = list(size = 8, opacity = 0.7),
  hovertemplate = paste(
    "<b>%{fullData.category}</b><br>",
    "Year: %{x}<br>",
    "Value: %{y:.2f}<br>",
    "<extra></extra>"
  )
) %>%
  layout(
    title = "Interactive Trends in Academic Research",
    xaxis = list(title = "Year"),
    yaxis = list(title = "Research Output Value"),
    hovermode = "closest"
  )

interactive_plot
```

## Data Tables

```{r data-table}
# Create an interactive data table
summary_table <- sample_data %>%
  group_by(year, category) %>%
  summarise(
    avg_value = mean(value),
    avg_impact = mean(impact_factor),
    n_observations = n(),
    .groups = "drop"
  )

datatable(
  summary_table,
  caption = "Summary by Year and Category",
  options = list(
    pageLength = 10,
    scrollX = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel')
  ),
  rownames = FALSE
) %>%
  formatRound(columns = c("avg_value", "avg_impact"), digits = 2)
```

# Statistical Analysis

```{r statistical-analysis}
# Perform statistical analysis
model <- lm(value ~ year + category + impact_factor, data = sample_data)
model_summary <- summary(model)

# Display model results
kable(
  broom::tidy(model),
  caption = "Linear Regression Results",
  digits = 3
)
```

The regression analysis reveals that `r paste(names(model$coefficients)[which(summary(model)$coefficients[,4] < 0.05)], collapse = ", ")` are significant predictors of the research output value (p < 0.05).

# Discussion

The results demonstrate the effectiveness of using R for academic data analysis within the journal publication workflow. Key findings include:

1. **Reproducibility**: All analyses can be reproduced by running the R code
2. **Integration**: Seamless integration with Jekyll publishing system
3. **Interactivity**: Support for interactive visualizations and tables
4. **Professional Output**: High-quality figures and tables suitable for publication

# Conclusion

This template provides a robust framework for data-driven academic publishing that combines the analytical power of R with the flexibility of Jekyll for web publication.

# References

<!-- References will be automatically generated from bibliography file -->

---

## Jekyll Integration Notes

To integrate this R Markdown file with Jekyll:

1. **Render the document**: `rmarkdown::render("article_template.Rmd")`
2. **Copy the generated markdown**: Move the `.md` file to the appropriate Jekyll collection folder
3. **Add Jekyll front matter**: The YAML header includes Jekyll-specific metadata
4. **Include media files**: Copy any generated plots to the media server location
5. **Update collections**: Ensure the collection is properly configured in `_config.yml`

## Required R Packages

Install the following packages before rendering:

```r
install.packages(c(
  "rmarkdown", "knitr", "ggplot2", "dplyr", 
  "plotly", "DT", "broom"
))
```